This is an example of article title

### 2019-08-29 paper.tex
textttt
10 things

@@

Tables support \texttt{map}, \texttt{reduce}, \texttt{groupreduce}, \texttt{groupby} and \texttt{join} operations.

@@

\subsection{Sort-based indexing}

@@

A distributed table is a distributed analogue of the one described
above. It is stored as many tables across multiple Julia processes,
\code{columns} returns a tuple of \emph{distributed arrays} and
\code{rows} returns a distributed array of tuples! The distributed
arrays implementation has the usual array operations (map, reduce,
hcat, vcat) defined on it in a distributed manner. Constructing a
table with one or more distributed columns using the table constructor
results in a distributed table. We use the word ``table'' from now on to refer interchangeably to both types of tables, unless
noted otherwise.

>>>>

Storing data row-by-row is not ideal when a query needs to operate on a small subset of fields for in such cases, one would have to load the whole dataset into memory and wade through it to find the relavent fields. But if we stored the columns separately, a single field's data is all available together and hence queries requiring data from a subset of fields load only data for those fields. The only advantage of row-by-row storage would be to read multiple fields per row on a sequential access optimized device such as tape drive or a spinning-disk hard drive. It's not worth worrying about these cases anymore.

The reason a table behaves as an iterator is a matter of convension. It's more helpful to think of writing code one row at a time. JuliaDB creates an immutable struct every time a row needs to be materialized. This may or may not lead to heap-allocation depending on the compiler optimizations that occur. In most cases the compiler is smart enough to eleminate allocation.

@@

Tables naturally support \texttt{map}, \texttt{reduce}, \texttt{groupreduce}, \texttt{groupby} and \texttt{join} operations. We will defer their discussion to the API documentation of JuliaDB. Read the Sectoin \ref{sec:sort} for more about the implementation of some of these operations.

@@

\subsection{Sort-based indexing}
\label{sec:sort}

@@

A distributed table is a distributed analogue of the one described
above. It is stored as many tables across multiple Julia processes,
\texttt{columns} returns a tuple of \emph{distributed arrays} and
\texttt{rows} returns a distributed array of tuples! The distributed
arrays implementation has the usual array operations (map, reduce,
hcat, vcat) defined on it in a distributed manner. Constructing a
table with one or more distributed columns using the table constructor
results in a distributed table. We use the word ``table'' from now on to refer interchangeably to both types of tables, unless
noted otherwise.
